### 2018-11-21 sections/conclusion.tex

A search for flavour-changing neutral-current decays of a top quark into an up-type quark ($q=u, c$) and the Standard Model Higgs boson, $t\to Hq$, is presented. 
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
CERN Large Hadron Collider and corresponding to an integrated luminosity of 36.1 fb$^{-1}$.
Two complementary analyses are performed to search for top-quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
and target the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$  decay modes, respectively.  
The $\Hbb$ search selects events with one isolated electron or muon from the $W \to \ell\nu$ decay, and multiple jets, with several 
of them being identified with high purity as originating from the hadronisation of $b$-quarks. 
The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
Both searches employ multivariate techniques to discriminate between the signal and the background on the basis of their different kinematics. 
No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
In the case of the $\Hbb$ search, the observed (expected) 95\% CL upper limits on the on the $t\to Hc$ and $t\to Hu$ branching ratios 
are $4.2 \times 10^{-3}\,(4.0 \times 10^{-3})$ and $5.2 \times 10^{-3}\,(4.9 \times 10^{-3})$, respectively.
In the case of the $\Htautau$ search, the observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios 
are $1.9 \times 10^{-3}\,(2.1 \times 10^{-3})$ and $1.7 \times 10^{-3}\,(2.0 \times 10^{-3})$, respectively.
The combination of these searches with ATLAS searches in diphoton and multilepton final states 
%significantly improves the sensitivity, 
yields observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), assuming respectively $\BR(t\to Hu)=0$ and $\BR(t\to Hc)=0$.
The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
%Upper limits in the $t\to Hc$ versus $t\to Hu$ branching ratio plane, as well as best-fit branching ratios, are also reported.
These are the most restrictive direct bounds on $tqH$ ($q=u,c$) interactions obtained so far.

>>>>

A search for flavour-changing neutral-current decays of a top quark into an up-type quark ($q=u, c$) and the Standard Model Higgs boson, $t\to Hq$, is presented. 
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
CERN Large Hadron Collider and corresponding to an integrated luminosity of 36.1 fb$^{-1}$.
Two complementary analyses are performed to search for top-quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
and target the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$  decay modes, respectively.  
The $\Hbb$ search selects events with one isolated electron or muon from the $W \to \ell\nu$ decay, and multiple jets, with several 
of them being identified with high purity as originating from the hadronisation of $b$-quarks. 
The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
Both searches employ multivariate techniques to discriminate between the signal and the background on the basis of their different kinematics. 
No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
In the case of the $\Hbb$ search, the observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios 
are $4.2 \times 10^{-3}\,(4.0 \times 10^{-3})$ and $5.2 \times 10^{-3}\,(4.9 \times 10^{-3})$, respectively.
In the case of the $\Htautau$ search, the observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios 
are $1.9 \times 10^{-3}\,(2.1 \times 10^{-3})$ and $1.7 \times 10^{-3}\,(2.0 \times 10^{-3})$, respectively.
The combination of these searches with ATLAS searches in diphoton and multilepton final states 
%significantly improves the sensitivity, 
yields observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), assuming $\BR(t\to Hu)=0$ and $\BR(t\to Hc)=0$ respectively.
The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
%Upper limits in the $t\to Hc$ versus $t\to Hu$ branching ratio plane, as well as best-fit branching ratios, are also reported.
These are the most restrictive direct bounds on $tqH$ ($q=u,c$) interactions obtained so far.

### 2018-11-21 sections/detector.tex

The ATLAS detector~\cite{PERF-2007-01} at the LHC covers almost the entire solid angle around the collision point,\footnote{ATLAS 
uses a right-handed coordinate system with its origin at the nominal interaction point (IP) in the 
centre of the detector.  
%and the $z$-axis coinciding with the axis of the beam pipe.
The $x$-axis points from
the IP to the centre of the LHC ring, %and
the $y$-axis points upward,
and the $z$-axis coincides with the axis of the beam pipe.
Cylindrical coordinates ($r$,$\phi$) are used 
in the transverse plane, $\phi$ being the azimuthal angle around the beam pipe. The pseudorapidity is defined in 
terms of the polar angle $\theta$ as $\eta = - \ln \tan(\theta/2)$.
Angular distance is measured in units of $\Delta R\equiv \sqrt{(\Delta\eta)^2+(\Delta\phi)^2}$.} and
consists of an inner tracking detector surrounded by a thin superconducting solenoid producing a
2~T axial magnetic field, electromagnetic and hadronic calorimeters, and a muon spectrometer
incorporating three large toroid magnet assemblies. The inner detector contains a high-granularity silicon pixel detector, 
including the %newly-installed
insertable B-layer~\cite{IBL}, installed in 2014,
and a silicon microstrip tracker,
together providing a precise reconstruction of tracks of charged particles in the pseudorapidity range $|\eta|<2.5$.
The inner detector also includes a transition radiation tracker that provides tracking and electron identification for $|\eta|<2.0$.
%The electromagnetic (EM) sampling calorimeter uses lead as the absorber material 
%and liquid-argon (LAr) as the active medium, and is divided into barrel ($|\eta|<1.475$) and end-cap ($1.375<|\eta|<3.2$) regions.  
%Hadron calorimetry is also based on the sampling technique, with either scintillator tiles or LAr as the active medium, and with 
%steel, copper, or tungsten as the absorber material. The calorimeters cover $|\eta|<4.9$. 
%Hadronic calorimetry is provided by the steel/scintillating-tile calorimeter,
%segmented into three barrel structures within $|\eta| < 1.7$, and two copper/LAr hadronic endcap calorimeters.
%The solid angle coverage is completed with forward copper/LAr and tungsten/LAr calorimeter modules
%optimised for electromagnetic and hadronic measurements respectively.
The calorimeter system covers the pseudorapidity range $|\eta| < 4.9$.
Within the region $|\eta|< 3.2$, electromagnetic (EM) calorimetry is provided by barrel and 
endcap high-granularity lead/liquid-argon (LAr) sampling calorimeters,
with an additional thin LAr presampler covering $|\eta| < 1.8$,
to correct for energy loss in material upstream of the calorimeters.
Hadronic calorimetry is provided by %the
a steel/scintillator-tile calorimeter,
segmented into three barrel structures within $|\eta| < 1.7$, and two copper/LAr hadronic endcap calorimeters.
The solid angle coverage is completed with forward copper/LAr and tungsten/LAr calorimeter modules
optimised for electromagnetic and hadronic measurements, respectively.
The calorimeters are surrounded by a muon spectrometer within a magnetic field provided by air-core toroid magnets 
with a bending integral of about 2.5 Tm in the barrel and up to 6 Tm in the endcaps. 
The muon spectrometer measures the trajectories of muons with $|\eta|<2.7$ using multiple layers of high-precision tracking chambers,
and is instrumented with separate trigger chambers covering $|\eta|<2.4$.
A two-level trigger system~\cite{Aaboud:2016leb}, consisting of a hardware-based level-1 trigger followed by 
a software-based high-level trigger, is used to reduce the event rate to a maximum of around 1 kHz for offline storage.

>>>>

The ATLAS detector~\cite{PERF-2007-01} at the LHC covers almost the entire solid angle around the collision point,\footnote{ATLAS 
uses a right-handed coordinate system with its origin at the nominal interaction point (IP) in the 
centre of the detector.  
%and the $z$-axis coinciding with the axis of the beam pipe.
The $x$-axis points from
the IP to the centre of the LHC ring, %and
the $y$-axis points upward,
and the $z$-axis coincides with the axis of the beam pipe.
Cylindrical coordinates ($r$,$\phi$) are used 
in the transverse plane, $\phi$ being the azimuthal angle around the beam pipe. The pseudorapidity is defined in 
terms of the polar angle $\theta$ as $\eta = - \ln \tan(\theta/2)$.
Angular distance is measured in units of $\Delta R\equiv \sqrt{(\Delta\eta)^2+(\Delta\phi)^2}$.} and
consists of an inner tracking detector surrounded by a thin superconducting solenoid producing a
2~T axial magnetic field, electromagnetic and hadronic calorimeters, and a muon spectrometer
incorporating three large toroid magnet assemblies. The inner detector contains a high-granularity silicon pixel detector, 
including the %newly-installed
insertable B-layer~\cite{IBL1,IBL2}, installed in 2014,
and a silicon microstrip tracker,
together providing a precise reconstruction of tracks of charged particles in the pseudorapidity range $|\eta|<2.5$.
The inner detector also includes a transition radiation tracker that provides tracking and electron identification for $|\eta|<2.0$.
%The electromagnetic (EM) sampling calorimeter uses lead as the absorber material 
%and liquid-argon (LAr) as the active medium, and is divided into barrel ($|\eta|<1.475$) and end-cap ($1.375<|\eta|<3.2$) regions.  
%Hadron calorimetry is also based on the sampling technique, with either scintillator tiles or LAr as the active medium, and with 
%steel, copper, or tungsten as the absorber material. The calorimeters cover $|\eta|<4.9$. 
%Hadronic calorimetry is provided by the steel/scintillating-tile calorimeter,
%segmented into three barrel structures within $|\eta| < 1.7$, and two copper/LAr hadronic endcap calorimeters.
%The solid angle coverage is completed with forward copper/LAr and tungsten/LAr calorimeter modules
%optimised for electromagnetic and hadronic measurements respectively.
The calorimeter system covers the pseudorapidity range $|\eta| < 4.9$.
Within the region $|\eta|< 3.2$, electromagnetic (EM) calorimetry is provided by barrel and 
endcap high-granularity lead/liquid-argon (LAr) sampling calorimeters,
with an additional thin LAr presampler covering $|\eta| < 1.8$,
to correct for energy loss in material upstream of the calorimeters.
Hadronic calorimetry is provided by %the
a steel/scintillator-tile calorimeter,
segmented into three barrel structures within $|\eta| < 1.7$, and two copper/LAr hadronic endcap calorimeters.
The solid angle coverage is completed with forward copper/LAr and tungsten/LAr calorimeter modules
optimised for electromagnetic and hadronic measurements, respectively.
The calorimeters are surrounded by a muon spectrometer within a magnetic field provided by air-core toroid magnets 
with a bending integral of about 2.5 Tm in the barrel and up to 6 Tm in the endcaps. 
The muon spectrometer measures the trajectories of muons with $|\eta|<2.7$ using multiple layers of high-precision tracking chambers,
and is instrumented with separate trigger chambers covering $|\eta|<2.4$.
A two-level trigger system~\cite{Aaboud:2016leb}, consisting of a hardware-based level-1 trigger followed by 
a software-based high-level trigger, is used to reduce the event rate to a maximum of around 1 kHz for offline storage.

### 2018-11-21 sections/statistical_analysis.tex

For each search, the final discriminant distributions across all analysis regions considered are jointly analysed to test for the 
presence of a signal. The statistical analysis uses a binned likelihood function ${\cal L}(\mu,\theta)$ constructed as
a product of Poisson probability terms over all bins considered in the search. This function depends
on the signal-strength parameter $\mu$, defined as a multiplicative factor to the yield for $\Hq$ signal events
normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=1\%$,
and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties of the signal and background expectations. 
Therefore, the expected total number of events in a given bin depends on $\mu$ and $\theta$. 
All nuisance parameters are subject to additional Gaussian or log-normal constraints in the likelihood, with the exception of a few parameters 
that control the normalisation of some background components (e.g. the \ttbin\ background in the case of the $\Hbb$ search), which 
are treated as free parameters in the fit.

@@

The fitting procedure is initially validated through extensive studies using mock data, defined as the sum of all predicted backgrounds 
plus an injected signal of variable strength, as well as by performing fits to real data where bins of the final discriminant variable with 
a signal contamination above 5\% are excluded (referred to as blinding requirements).
In both cases, the robustness of the model for systematic uncertainties is established by verifying the stability of the fitted background 
when varying assumptions on some of the leading sources of uncertainty. 
After this, the blinding requirements
are removed in the data and a fit under the signal-plus-background hypothesis is performed. Further checks involve the comparison of the fitted 
nuisance parameters before and after removal of the blinding requirements, which are found to be consistent. In addition, it is verified that the 
fit is able to correctly determine the strength of a simulated signal injected in the real data.

The test statistic $q_\mu$ is defined as the profile likelihood ratio, 
$q_\mu = -2\ln({\cal L}(\mu,{\hat{\theta}}_\mu)/{\cal L}(\hat{\mu},\hat{\theta}))$,
where $\hat{\mu}$ and $\hat{\theta}$ are the values of the parameters that
maximise the likelihood function (subject to the constraint $0\leq \hat{\mu} \leq \mu$), and ${\hat{\theta}}_\mu$ are the values of the
nuisance parameters that maximise the likelihood function for a given value of $\mu$. 
The test statistic $q_\mu$ is evaluated with the {\textsc RooFit} package~\cite{Verkerke:2003ir,RooFitManual}.
A related statistic is used to determine the compatibility of the observed data with the background-only hypothesis (the so-called discovery test)  
by setting $\mu=0$ in the profile likelihood ratio and leaving $\hat{\mu}$ unconstrained: $q_0 = -2\ln({\cal L}(0,{\hat{\theta}}_0)/{\cal L}(\hat{\mu},\hat{\theta}))$.
The $p$-value (referred to as $p_0$) representing the probability of the data being compatible with the background-only hypothesis is estimated by integrating
%the distribution of $q_0$ obtained from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js}, 
the distribution of $q_0$ based on the asymptotic formulae in Ref.~\cite{Cowan:2010js}, 
above the observed value of $q_0$ in the data. 
%The observed $p_0$-value is checked for each explored signal scenario.
In the case of the data being compatible with the background-only hypothesis, upper limits on $\mu$, and thus on 
$\BR(t\to Hq)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
For a given signal scenario, values of the $\BR(t\to Hq)$ yielding CL$_{\textrm{s}} < 0.05$, 
where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded at $\geq 95\%$ CL.

>>>>

For each search, the final discriminant distributions across all analysis regions considered are jointly analysed to test for the 
presence of a signal. The statistical analysis uses a binned likelihood function ${\cal L}(\mu,\theta)$ constructed as
a product of Poisson probability terms over all bins considered in the search. This function depends
on the signal-strength parameter $\mu$, defined as a factor multiplying the yield of $\Hq$ signal events
normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=1\%$,
and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties on the signal and background expectations. 
Therefore, the expected total number of events in a given bin depends on $\mu$ and $\theta$. 
All nuisance parameters are subject to additional Gaussian or log-normal constraints in the likelihood, with the exception of a few parameters 
that control the normalisation of some background components (e.g.\ the \ttbin\ background in the case of the $\Hbb$ search), which 
are treated as free parameters in the fit.

@@

The fitting procedure was initially validated through extensive studies using mock data, defined as the sum of all predicted backgrounds 
plus an injected signal of variable strength, as well as by performing fits to real data where bins of the final discriminant variable with 
a signal contamination above 5\% are excluded (referred to as blinding requirements).
In both cases, the robustness of the model for systematic uncertainties is established by verifying the stability of the fitted background 
when varying assumptions about some of the leading sources of uncertainty. 
After this, the blinding requirements
are removed in the data and a fit under the signal-plus-background hypothesis is performed. Further checks involve the comparison of the fitted 
nuisance parameters before and after removal of the blinding requirements, and their values are found to be consistent. In addition, it is verified that the 
fit is able to correctly determine the strength of a simulated signal injected into the real data.

The test statistic $q_\mu$ is defined as the profile likelihood ratio, 
$q_\mu = -2\ln({\cal L}(\mu,{\hat{\theta}}_\mu)/{\cal L}(\hat{\mu},\hat{\theta}))$,
where $\hat{\mu}$ and $\hat{\theta}$ are the values of the parameters that
maximise the likelihood function (subject to the constraint $0\leq \hat{\mu} \leq \mu$), and ${\hat{\theta}}_\mu$ are the values of the
nuisance parameters that maximise the likelihood function for a given value of $\mu$. 
The test statistic $q_\mu$ is evaluated with the {\textsc RooFit} package~\cite{Verkerke:2003ir,RooFitManual}.
A related statistic is used to determine whether the observed data is compatible with the background-only hypothesis (the so-called discovery test)  
by setting $\mu=0$ in the profile likelihood ratio and leaving $\hat{\mu}$ unconstrained: $q_0 = -2\ln({\cal L}(0,{\hat{\theta}}_0)/{\cal L}(\hat{\mu},\hat{\theta}))$.
The $p$-value (referred to as $p_0$) representing the probability of the data being compatible with the background-only hypothesis is estimated by integrating
%the distribution of $q_0$ obtained from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js}, 
the distribution of $q_0$ based on the asymptotic formulae in Ref.~\cite{Cowan:2010js}, 
above the observed value of $q_0$ in the data. 
%The observed $p_0$-value is checked for each explored signal scenario.
In the case of the data being compatible with the background-only hypothesis, upper limits on $\mu$, and thus on 
$\BR(t\to Hq)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
For a given signal scenario, values of the $\BR(t\to Hq)$ yielding CL$_{\textrm{s}} < 0.05$, 
where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded at $\geq 95\%$ CL.
